
```{r}
#| echo: false
#| message: false
googledrive::drive_auth(email = Sys.getenv("GMAIL_ROG"))

if (!dir.exists('csv')) {
  dir.create('csv')
}

csv_fn <- "csv/sched.csv"

googledrive::drive_download(
    file = 'PSYCH-260.001-2025-Fall',
  path = csv_fn,
  type = 'csv',
  overwrite = TRUE
)

if (file.exists(csv_fn)) {
  sched_df <- readr::read_csv(csv_fn, show_col_types = FALSE)
} else {
  message("File not found: ", csv_fn)
  sched_df <- NULL
}

sched_df <- sched_df |>
  dplyr::mutate(class_day_1 = lubridate::as_date(class_date_1),
                class_day_2 = lubridate::as_date(class_date_2))
```

```{r}
#| label: helper-functions
#| echo: false
#| message: false
#| 
prettify_date <- function(date) {
  paste0(
    lubridate::wday(date, label = TRUE), ", ",
    lubridate::month(date, label = TRUE),
    " ",
    lubridate::day(date),
    ", ",
    lubridate::year(date)
  )
}
```

::: {.callout-note}
Textbook reading assignments in the Watson & Breedlove text, *The Mind's Machine* will be indicated by the following shorthand: 'MM pp 3-15'.
This means to read pages 3 to 15.

Note that the text covers material we won't cover in class.
If we don't cover material in class, you aren't responsible for it.
That said, you may find it interesting to learn and know about anyway.
:::

## `{r} sched_df$week[1]` {- #week-01}

### `{r} prettify_date(sched_df$class_day_1[1])` {-}

*`{r} sched_df$class_1_theme[1]`*

- *Read*: MM pp 3-16
- *Slides*: | [html](slides/wk-01-2025-08-26-intro.qmd) |

### `{r} prettify_date(sched_df$class_day_2[1])` {-}

*`{r} sched_df$class_2_theme[1]`*

- *Read*: MM pp 3-16
- *Watch*: @National_Geographic2014-gv, @NeuroBriefs2011-pd, @Eames_Office2010-xd
- *Slides*: | [html](slides/wk-01-2025-08-28-hist-methods.qmd) |

## `{r} sched_df$week[2]` {- #week-02}

### `{r} prettify_date(sched_df$class_day_1[2])` {-}

*`{r} sched_df$class_1_theme[2]`*

- *Read*: MM pp 44-50
- *Watch*: @National-Institute-on-Biomedical-Imaging-and-BioengineeringUnknown-vz, @Video2010-jw, @Understanding_Animal_Research2009-vq
- *Slides*: | [html](slides/wk-02-2025-09-02-methods.qmd) |

### `{r} prettify_date(sched_df$class_day_2[2])` {-}

*`{r} sched_df$class_2_theme[2]`*

- *Read*: MM pp 27-44
- Extra credit assignment due: [Canvas dropbox](https://psu.instructure.com/courses/2415710/assignments/17605818)
- *Slides*:  | [html](slides/wk-02-2025-09-04-anatomy-I.qmd) |

## `{r} sched_df$week[3]` {- #week-03}

### `{r} prettify_date(sched_df$class_day_1[3])` {-}

*`{r} sched_df$class_1_theme[3]`*

- *Read*: MM pp 16-27
- *Slides*:  | [html](slides/wk-03-2025-09-09-anatomy-II.qmd) |

### `{r} prettify_date(sched_df$class_day_2[3])` {-}

*`{r} sched_df$class_2_theme[3]`*

- *Slides*:  | [html](slides/wk-03-2025-09-11-anatomy-III.qmd) |

## `{r} sched_df$week[4]` {- #week-04}

### `{r} prettify_date(sched_df$class_day_1[4])` {-}

*`{r} sched_df$class_1_theme[4]`*

- *Read*: MM pp 20-27
- *Slides*:  | [html](slides/wk-04-2025-09-16-cellular-neuro.qmd) |

### `{r} prettify_date(sched_df$class_day_2[4])` {-}

*`{r} sched_df$class_2_theme[4]`*

- *Read*: MM pp 58-74
- *Slides*:  | [html](slides/wk-04-2025-09-18-neurophys.qmd) |

## `{r} sched_df$week[5]` {- #week-05}

### `{r} prettify_date(sched_df$class_day_1[5])` {-}

*`{r} sched_df$class_1_theme[5]`*

- *Slides*: | [html](slides/wk-05-2025-09-23-exam-rev.qmd) |

### `{r} prettify_date(sched_df$class_day_2[5])` {-}

*`{r} sched_df$class_2_theme[5]`*

## `{r} sched_df$week[6]` {- #week-06}

### `{r} prettify_date(sched_df$class_day_1[6])` {-}

*`{r} sched_df$class_1_theme[6]`*

- *Read*: MM pp 86-100
- *Slides*:  | [html](slides/wk-06-2025-09-30-neurochem.qmd) |

### `{r} prettify_date(sched_df$class_day_2[6])` {-}

*`{r} sched_df$class_2_theme[6]`*

## `{r} sched_df$week[7]` {- #week-07}

### `{r} prettify_date(sched_df$class_day_1[7])` {-}

*`{r} sched_df$class_1_theme[7]`*

- *Read*: MM pp 102-106, 122-123
- *Slides*:  | [html](slides/wk-07-2025-10-07-neurochem-II.qmd) |

### `{r} prettify_date(sched_df$class_day_2[7])` {-}

*`{r} sched_df$class_2_theme[7]`*

- *Read*: MM pp 248-266
- *Slides*:  | [html](slides/wk-07-2025-10-09-hormones.qmd) |

## `{r} sched_df$week[8]` {- #week-08}

### `{r} prettify_date(sched_df$class_day_1[8])` {-}

*`{r} sched_df$class_1_theme[8]`*

- *Slides*:  | [html](slides/wk-08-2025-10-14-evolution.qmd) |
- *Watch*: @Scale-2023-gp

### `{r} prettify_date(sched_df$class_day_2[8])` {-}

*`{r} sched_df$class_2_theme[8]`*

- *Read*: MM pp 124-134, 145
- *Slides*:  | [html](slides/wk-08-2025-10-16-development.qmd) |

## `{r} sched_df$week[9]` {- #week-09}

### `{r} prettify_date(sched_df$class_day_1[9])` {-}

*`{r} sched_df$class_1_theme[9]`*

- *Slides*:  | [html](slides/wk-09-2025-10-21-exam-rev.qmd) |

### `{r} prettify_date(sched_df$class_day_2[9])` {-}

*`{r} sched_df$class_2_theme[9]`*

## `{r} sched_df$week[10]` {- #week-10}

### `{r} prettify_date(sched_df$class_day_1[10])` {-}

*`{r} sched_df$class_1_theme[10]`*

- *Slides*:  | [html](slides/wk-10-2025-10-28-psychopathology-I.qmd) |


### `{r} prettify_date(sched_df$class_day_2[10])` {-}

*`{r} sched_df$class_2_theme[10]`*

## `{r} sched_df$week[11]` {- #week-11}

### `{r} prettify_date(sched_df$class_day_1[11])` {-}

*`{r} sched_df$class_1_theme[11]`*

### `{r} prettify_date(sched_df$class_day_2[11])` {-}

*`{r} sched_df$class_2_theme[11]`*

## `{r} sched_df$week[12]` {- #week-12}

### `{r} prettify_date(sched_df$class_day_1[12])` {-}

*`{r} sched_df$class_1_theme[12]`*

### `{r} prettify_date(sched_df$class_day_2[12])` {-}

*`{r} sched_df$class_2_theme[12]`*

## `{r} sched_df$week[13]` {- #week-13}

### `{r} prettify_date(sched_df$class_day_1[13])` {-}

*`{r} sched_df$class_1_theme[13]`*

### `{r} prettify_date(sched_df$class_day_2[13])` {-}

*`{r} sched_df$class_2_theme[13]`*

## `{r} sched_df$week[14]` {- #week-14}

### NO CLASS

## `{r} sched_df$week[15]` {- #week-15}

### `{r} prettify_date(sched_df$class_day_1[15])` {-}

*`{r} sched_df$class_1_theme[15]`*

### `{r} prettify_date(sched_df$class_day_2[15])` {-}

*`{r} sched_df$class_2_theme[15]`*

## `{r} sched_df$week[16]` {- #week-16}

### `{r} prettify_date(sched_df$class_day_1[16])` {-}

*`{r} sched_df$class_1_theme[16]`*

### `{r} prettify_date(sched_df$class_day_2[16])` {-}

*`{r} sched_df$class_2_theme[16]`*

## `{r} sched_df$week[17]` {- #finals-week}

### Tue, Dec 16, 2025

*Exam 4 (Final)*, 4:40-6:30 pm in 114 Steidle